---
title: "How to use R Markdown"
author: "Hoon Kim"
date: "09/01/2021"
output: html_document
---

# Write your own comments
## Write your own comments
### Write your own comments
#### Write your own comments
##### Write your own comments
###### Write your own comments


## A short introduction on how to use R Markdown

A short introduction on how to use R Markdown is available at [rmarkdown](https://rmarkdown.rstudio.com/lesson-1.html).

You don't need to go over all chapters in [rmarkdown](https://rmarkdown.rstudio.com/lesson-1.html), and I think the following short chapters will be sufficient for our course.

- **Introduction**
- **How It Works**
- **Code Chunks**
- **Inline Code**
- **Code Languages**
- **Parameters**
- **Tables**
- **Markdown Basics**


## Load a R package
```{r include = FALSE}
library(viridis)
```

The code below deomostrates two color paletters in the [viridis](https://github.com/sjmgarier/viridis) package. Each plot displayes a contour map of the Mounga Wau volcano in Auckland, New Zealand.


## Viridis colors

```{r}

image(volcano, col = viridis(200))

```


## Magma colors
```{r}

image(volcano, col = viridis(200, option = "A"))

```

## Run a shell command
```{bash}

ls -al

```


```{bash}

echo $PWD

```

